\cvsection{Work Experience}
\begin{cventries}
    \cventry
		{\large Software Engineer 3 | Platform Software | Embedded \& Avionics Systems}
	{\href{https://www.boeing.co.in/}{\large Boeing India Pvt. Ltd.}}
	{\large Bengaluru, India}
	{\large Nov'19 - Present}
	{
		\vspace{0.25cm}
		\begin{cvitems}
		\item{\large Delivered platform software across \textbf{Cockpit Displays, Common Core, Compute Platform, and Cabin Experience systems} on heterogeneous hardware, building \textbf{Linux} and \textbf{RTOS}-based real-time services with strong focus on reliability, observability, and cross-system integration.}
		\vspace{0.25cm}
		\item{\large Designed scalable backend architectures, service interfaces, and data models, translating complex system requirements into modular APIs and production-ready services while collaborating across teams to drive standards, maintainability, and design consistency.}
		\vspace{0.25cm}
		\item{\large Built containerized services and automation workflows on Linux platforms, leading end-to-end development from feasibility and architecture through implementation and code reviews, ensuring traceable, testable, and maintainable software delivery.}
		\vspace{0.25cm}
		\item{\large Developed platform infrastructure including middleware, communication frameworks, and diagnostic tooling, optimizing performance, fault tolerance, and data handling across distributed environments and hardware-in-loop test systems.}
		\vspace{0.25cm}
		\item{\large Implemented CI/CD pipelines using GitLab CI and Docker, automating build, integration, and deployment workflows to improve release velocity, reproducibility, and overall system stability across multiple product lines.}
		\vspace{0.25cm}
		\item{\large Configured custom hardware architectures and optimized Board Support Packages, including U‐Boot, kernel, custom Yocto recipe‐based root file systems, cross‐compilation toolchains, and device trees, to enable efficient secure boot processes and enhance runtime performance for custom hardware platforms.}
		\vspace{0.25cm}
		\end{cvitems}
	}
    \cventry
    {\large Flight Software Engineer | Integrated Avionics | Command \& Data Handling | Guidance, Navigation \& Control}
	{\href{http://www.teamindus.in/}{\large Team Indus (Axiom Research Labs Pvt. Ltd.)}}
	{\large Bengaluru, India}
	{\large Jul.'17 - Present, \textbf{Intern}: Jan.'17 - Jun.'17}
	{
		\vspace{0.25cm}
		\begin{cvitems}
		\item{\large Developing software systems for \textbf{orbital, descent and surface} phases of the soft landing lunar mission, with onboard state estimation, autonomous attitude correction, lunar terrain feature tracking, active thermal and power control, interface drivers for sensors peripherals and other interfacing cards, with limited fault detection, isolation, and recovery.}
		\vspace{0.25cm}
		\item{\large Developed software system to perform an autonomous lunar descent sequence, with the onboard estimation of lander states, constrained landing site selection, targeted descent to the selected landing site and mode transition logic.}
		\vspace{0.25cm}
		\item{\large Design and development of onboard data handling telemetry \& telecommand packet definition for the entire lunar landing mission: real-time, absolute time-tagged, patch, differential time-tagged, configurable block and event-based.}
		\vspace{0.25cm}
		\item{\large Developing frameworks for running regression unit, interface and integration level of testing with auto code generation capabilities which involves sensor and other interface cards emulation using Interface Emulation Card (IEC)\href{http://zedboard.org/product/microzed/}, board bring-ups for Integrated Avionics Unit (IAU), and generate reports for each activity.}
		\vspace{0.25cm}
		\item{\large Developed framework for Processor in Loop Simulation (PiLS) system emulating sensor and actuator electrical interfaces to IAU.}
		\vspace{0.25cm}
		\end{cvitems}
	}
%    \cventry
%    {}
%	{}
%	{}
%	{}
%	{
%		\begin{cvitems}
			%\item{Maintain a complete dashboard for Flight Software team for coverage on code development, documentation and post-tests analysis.}
			%\item{Review Software artefacts created by the team members from time to time for \textbf{JPL} code compliance and \textbf{MISRA C - 2014} guidelines.}
	%\item{\large Writing, analyzing, and maintenance of software requirements for Lander On-Board Computer(L-OBC), Auxillary Flight Computer (L-AFC) and Rover On-Board Computer(R-OBC). Studying the feasibility with present architecture, providing solutions for each module development and final independent verification and validation.}
			%\item{\large Interface drivers for protocol establishment with the \textbf{(L-OBC)}\href{http://ww1.microchip.com/downloads/en/DeviceDoc/ATF697FF.pdf}, \textbf{L-AFC}\href{http://zedboard.org/product/zedboard}, \textbf{R-OBC}\href{http://zedboard.org/product/zedboard}, other interfacing cards and sensors.}
			%\item{\large Developed software system to perform an \textbf{autonomous lunar descent sequence}, with the onboard estimation of lander states, constrained landing site selection, targeted descent to the selected landing site and mode transition logic.}
			%\item{Developing Lander OBC boot architecture, custom linkers, make system and maintaining different configurations for Atmel's RAD Hard \textbf{ATF697FF} - \textbf{SPARC V8} processor operated as bare metal with \textbf{Round Robin} scheduler}
			%\item{\large Developing frameworks for running regression unit, interface and integration level of testing with auto code generation capabilities which involves sensor and other interface cards emulation using \textbf{Interface Emulation Card (IEC)}\href{http://zedboard.org/product/microzed/}, board bring-ups for \textbf{Integrated Avionics Unit (IAU)}, and generate reports for each activity.}
%			%\item{Developing Lander OBC boot architecture, custom linkers, make system and maintaining different configurations for Atmel's RAD Hard \textbf{ATF697FF} - \textbf{SPARC V8} processor operated as bare metal with \textbf{Round Robin} scheduler}
%			\item{\large Developing frameworks for running regression unit, interface and integration level of testing with auto code generation capabilities which involves sensor and other interface cards emulation using \textbf{Interface Emulation Card (IEC)}\href{http://zedboard.org/product/microzed/}, board bring-ups for \textbf{Integrated Avionics Unit (IAU)}, and generate reports for each activity.}
%			\item{\large Developed framework for \textbf{Processor in Loop Simulation (PiLS)} system emulating sensor and actuator electrical interfaces to IAU.}
%			%\item{Maintain a complete dashboard for Flight Software team for coverage on code development, documentation and post-tests analysis.}
%			%\item{Review Software artefacts created by the team members from time to time for \textbf{JPL} code compliance and \textbf{MISRA C - 2014} guidelines.}
%		\end{cvitems}
%	}

\end{cventries}
